Hierarchical wrinkling in a confined permeable biogel

### 2015-01-25 fig_plis/article_plis.tex
Réorganise les Supplementary pour coller à l'ordre du texte principal

Figure~\ref{fig:sideview}a shows confocal measurements in the case where both top and bottom walls have been coated. Starting from a homogeneous solution (first panel Fig.~\ref{fig:sideview}a where black margins correspond to the glass walls), the gel forms and simultaneously expels solvent on both sides. Since two interfaces clearly separate a protein-rich phase and a protein-poor phase, we model the resulting situation as a porous elastic film of thickness $h$ sandwiched between two viscous layers of respective thicknesses $H_1$ and $H_2$ in a cell of thickness $e=H_1+h+H_2$ (Fig.~\ref{fig:sideview}b). Wavelength being much larger than thickness, we can assume small strain in the film and lubrication in the layers. Relative increase in protein concentration during syn\ae{}resis can be deduced from the brighter fluorescence in the second panel of Fig.~\ref{fig:sideview}a. Extracting the top and bottom surface of the gel phase allows for quantitative measurements of the relative volume (Fig.~\ref{fig:sideview}c) and excess surface area of the gel film (Fig.~\ref{fig:sideview}d). This confirms that the instability is due to swelling.

@@

\begin{figure*}
	\includegraphics{nonmonotonic}%
	\caption{Microstructure evolution. (a) Details of confocal images in fully adhesive conditions (left) and with no adhesion on top (right). Scale bar is \SI{10}{\micro\metre}. Arrows indicates the pore size. (b) Corresponding Fourier spectra in second situation and same times. Lines are fits by Eq.~\ref{eq:fractalS}. (c-d) Evolution of susceptibility and fractal dimension in both situations (black line and orange dashed line respectively). Symbols indicates the times of the images in (a).}%
	\label{fig:nonmonotonic}%
\end{figure*}

>>>>

Figure~\ref{fig:sideview}a shows confocal measurements in the case where both top and bottom walls have been coated. Starting from a homogeneous solution (first panel Fig.~\ref{fig:sideview}a where black margins correspond to the glass walls), the gel forms and simultaneously expels solvent on both sides. Since two interfaces clearly separate a protein-rich phase and a protein-poor phase, we model the resulting situation as a porous elastic film of thickness $h$ sandwiched between two viscous layers of respective thicknesses $H_1$ and $H_2$ in a cell of thickness $e=H_1+h+H_2$ (Fig.~\ref{fig:sideview}b). Wavelength being much larger than thickness, we can assume small strain in the film and lubrication in the layers. Relative increase in protein concentration during syn\ae{}resis can be deduced from the brighter fluorescence in the second panel of Fig.~\ref{fig:sideview}a. Extracting the top and bottom surface of the gel phase allows for quantitative measurements of the relative volume (Fig.~\ref{fig:sideview}c) and excess surface area of the gel film (Fig.~\ref{fig:sideview}d) (see Supplementary Methods). This confirms that the instability is due to swelling.

@@

\begin{figure}
	\includegraphics{nonmonotonic}%
	\caption{Microstructure evolution. (a) Details of confocal images in fully adhesive conditions (top row) and with no adhesion on top (bottom row). Scale bar is \SI{10}{\micro\metre}. Arrows indicates the pore size. (b) Corresponding Fourier spectra in second situation and same times. Lines are fits by Eq.~\ref{eq:fractalS}. (c-d) Evolution of susceptibility and fractal dimension in both situations (black line and orange dashed line respectively). Symbols indicates the times of the images in (a).}%
	\label{fig:nonmonotonic}%
\end{figure}
